### 2020-08-20 ReadMe.rmd
updates
try fix GA
update readme

![Docker image build](https://github.com/VLucet/landchange-connectivity-monteregie/workflows/Build%20/%20Push%20Docker%20image/badge.svg)

@@

[GitHub page (latest)](https://vlucet.github.io/landchange-connectivity-monteregie/)

[Thesis PDF (latest)](https://github.com/VLucet/landchange-connectivity-monteregie/blob/master/thesis/build/thesis.pdf)

[Initial submission release](https://github.com/VLucet/landchange-connectivity-monteregie/)

@@

This repository contains all the code and some of the data that is needed to reproduce the work of my MSc Thesis titled: **Integrating land use and land cover change simulations and connectivity modeling: a case study in the Montérégie region in southern Québec.** It is package under the form of a [Docker image](https://docs.docker.com/engine/reference/commandline/image/) and makes use of the [`renv`](https://rstudio.github.io/renv/articles/renv.html) package.

@@

*****
#### How to reproduce this thesis

@@

#### Docker image detailed breakdwon

#### renv lockfile breakdown

>>>>

![Docker image build](https://github.com/VLucet/landchange-connectivity-monteregie/workflows/Build%20/%20Push%20Docker%20image/badge.svg)
![CI - All Figures](https://github.com/VLucet/landchange-connectivity-monteregie/workflows/CI%20-%20All%20Figures/badge.svg)

@@

| [GitHub page (latest)](https://vlucet.github.io/landchange-connectivity-monteregie/) | [Thesis PDF (latest)](https://github.com/VLucet/landchange-connectivity-monteregie/blob/master/thesis/build/thesis.pdf) | [Initial submission release](https://github.com/VLucet/landchange-connectivity-monteregie/)
|:-------------:|:-------------:|:-----:|

@@

This repository contains all the code and some of the data that is needed to reproduce the work of my MSc Thesis titled:

> **Integrating land use and land cover change simulations and connectivity modeling: a case study in the Montérégie region in southern Québec.**

It is packaged under the form of a [Docker image](https://docs.docker.com/engine/reference/commandline/image/) and makes use of the [`renv`](https://rstudio.github.io/renv/articles/renv.html) package.

@@

**Most of the figures in the thesis are reproducible**. This repo is set up for continuous deployment of a [github page](https://vlucet.github.io/landchange-connectivity-monteregie/) that contains the main figures in the thesis.

*****
### Reproducibility

@@

<!-- #### Docker image detailed breakdwon -->

<!-- ***** -->

<!-- #### renv lockfile breakdown -->

<!-- ***** -->
